Cooperative Control for Narrow Passage Traversal with an Ornithopter Micro Air Vehicle and Lightweight Ground Station

### 2012-10-10 manuscript.tex
Update H2Bird drawing, abstract

% This is "aamas2013 .tex" September 2012 
% This file should be compiled with "aamas2013 .cls" 
% This example file demonstrates the use of the 'aamas2013 .cls'
% LaTeX2e document class file. It is for those submitting
% articles to AAMAS 2013  conference. This file is based on
% the sig-alternate.tex example file.
% The 'sig-alternate.cls' file of ACM will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
% than the original style ACM style.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls ) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with AAMAS data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'aamas2013 .cls' you don't have control
% from within the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the IFAAMAS Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% These information will be overwritten by fixed AAMAS 2013  information
% in the style files - it is NOT as you are used with ACM style files.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%

% This is the document class for full camera ready papers and extended abstracts repsectively

@@

% AUTHORS

% For initial submission, do not give author names, but the
% tracking number, instead, as the review process is blind.

@@

%\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%

@@

We also introduce a new ornithopter MAV, the 13 gram H$^2$Bird. It features clap and fling wings, improves upon a previous design by utilizing a carbon fiber airframe, tail rotor, and elevator, and carries a payload of 2.8 grams. We augment the ornithopter's built-in gyroscope-based control with a ground station, which has power and weight requirements appropriate for deployment on a ground vehicle. The ground station provides heading estimates to the ornithoper by running a real-time motion tracking algorithm on a live video stream. This allows the ornithopter to reliably negotiate flight through narrow openings.

@@

% Note that the category section should be completed after reference to the ACM Computing Classification Scheme available at
% http://www.acm.org/about/class/1998/.

@@

%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

%General terms should be selected from the following 16 terms: Algorithms, Management, Measurement, Documentation, Performance, Design, Economics, Reliability, Experimentation, Security, Human Factors, Standardization, Languages, Theory, Legal Aspects, Verification.

@@

%Keywords are your own choice of terms you would like the paper to be indexed by.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%TODO(ryan)
The power, size, and weight constraints of micro air vehicle (MAV) platforms significantly limit on-board sensing and computational resources, and thus the complexity of the control and state estimation algorithms which can be executed on-board. These constraints are particularly severe for flapping wing MAVs offer the promise of superior safety, efficiency, and noise profile to rotor craft MAVs, but at the expense of payload weight.
\begin{figure}[!tb]
\centering
\includegraphics[width=\linewidth]{figures/h2bird.png}
\caption{H$^2$Bird Ornithopter MAV}
\label{fig:h2bird}
\end{figure}

@@

The step response exhibits a rise time of approximately 1.4 seconds. The H$^2$Bird flies at an average forward velocity of 1.2 m/s, so the estimated minimum turning radius of the robot is 1.07 meters.

@@

%%
%% The following two commands are all you need in the
%% initial runs of your .tex file to
%% produce the bibliography for the citations in your paper.
%\bibliographystyle{abbrv}
%\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
%% You must have a proper ".bib" file
%%  and remember to run:
%% latex bibtex latex latex
%% to resolve all references
%%
%% ACM needs 'a single self-contained file'!
%%
%%APPENDICES are optional
%%\balancecolumns
%\appendix
%%Appendix A
%\section{Headings in Appendices}
%The rules about hierarchical headings discussed above for
%the body of the article are different in the appendices.
%In the \textbf{appendix} environment, the command
%\textbf{section} is used to
%indicate the start of each Appendix, with alphabetic order
%designation (i.e. the first is A, the second B, etc.) and
%a title (if you include one).  So, if you need
%hierarchical structure
%\textit{within} an Appendix, start with \textbf{subsection} as the
%highest level. Here is an outline of the body of this
%document in Appendix-appropriate form:
%\subsection{Introduction}
%\subsection{The Body of the Paper}
%\subsubsection{Type Changes and  Special Characters}
%\subsubsection{Math Equations}
%\paragraph{Inline (In-text) Equations}
%\paragraph{Display Equations}
%\subsubsection{Citations}
%\subsubsection{Tables}
%\subsubsection{Figures}
%\subsubsection{Theorem-like Constructs}
%\subsubsection*{A Caveat for the \TeX\ Expert}
%\subsection{Conclusions}
%\subsection{Acknowledgments}
%\subsection{Additional Authors}
%This section is inserted by \LaTeX; you do not insert it.
%You just add the names and information in the
%\texttt{{\char'134}additionalauthors} command at the start
%of the document.
%\subsection{References}
%Generated by bibtex from your ~.bib file.  Run latex,
%then bibtex, then latex twice (to resolve references)
%to create the ~.bbl file.  Insert that ~.bbl file into
%the .tex source file and comment out
%the command \texttt{{\char'134}thebibliography}.
%% This next section command marks the start of
%% Appendix B, and does not continue the present hierarchy
%\section{More Help for the Hardy}
%The aamas2013 .cls file is based on the
%sig-alternate.cls file that is itself chock-full of succinct and
%helpful comments.  If you consider yourself a moderately experienced
%to expert user of \LaTeX, you may find reading it useful but please
%remember not to change it.
%%\balancecolumns % GM June 2007
%% That's all folks!
\end{document}

>>>>

% This is "aamas2013 .tex" September 2012 
% This file should be compiled with "aamas2013 .cls" 
% This example file demonstrates the use of the 'aamas2013 .cls'
% LaTeX2e document class file. It is for those submitting
% articles to AAMAS 2013  conference. This file is based on
% the sig-alternate.tex example file.
% The 'sig-alternate.cls' file of ACM will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
% than the original style ACM style.
%
% ----------------------------------------------------------------------
% This .tex file (and associated .cls ) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with AAMAS data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'aamas2013 .cls' you don't have control
% from within the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the IFAAMAS Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% These information will be overwritten by fixed AAMAS 2013  information
% in the style files - it is NOT as you are used with ACM style files.
%
% ----------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%

% This is the document class for full camera ready papers and extended 
% abstracts repsectively

@@

% AUTHORS
% For initial submission, do not give author names, but the
% tracking number, instead, as the review process is blind.

@@

%\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors 
% section.
%

@@

We also introduce a new ornithopter MAV, the 13 gram H$^2$Bird. It 
features clap and fling wings, improves upon a previous design by 
utilizing a carbon fiber airframe, tail rotor, and elevator, and carries a 
payload of 2.8 grams. We augment the ornithopter's built-in 
gyroscope-based control with a ground station, which has power and weight 
requirements appropriate for deployment on 30 gram a ground vehicle. The ground 
station provides heading estimates to the ornithoper by running a 
real-time motion tracking algorithm on a live video stream. This allows 
the ornithopter to reliably negotiate flight through narrow openings.

@@

% Note that the category section should be completed after reference to 
% the ACM Computing Classification Scheme available at
% http://www.acm.org/about/class/1998/.

@@

% A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, 
% performance measures]

% General terms should be selected from the following 16 terms: 
% Algorithms, Management, Measurement, Documentation, Performance, 
% Design, Economics, Reliability, Experimentation, Security, 
% Human Factors, Standardization, Languages, Theory, Legal Aspects, 
% Verification.

@@

% Keywords are your own choice of terms you would like the paper to be indexed 
% by.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%TODO(ryan)
The power, size, and weight constraints of micro air vehicle (MAV) 
platforms significantly limit on-board sensing and computational 
resources, and thus the complexity of the control and state estimation 
algorithms which can be executed on-board. These constraints are 
particularly severe for flapping wing MAVs offer the promise of superior 
safety, efficiency, and noise profile to rotor craft MAVs, but at the 
expense of payload weight.

\begin{figure}[!tb]
\centering
\includegraphics[width=\linewidth]{figures/h2bird.png}
\caption{H$^2$Bird Ornithopter MAV}
\label{fig:h2bird}
\end{figure}

@@

The step response exhibits a rise time of approximately 1.4 seconds. The H
$^2$Bird flies at an average forward velocity of 1.2 m/s, so the estimated 
minimum turning radius of the robot is 1.07 meters.

@@

%%
%% The following two commands are all you need in the
%% initial runs of your .tex file to
%% produce the bibliography for the citations in your paper.
%\bibliographystyle{abbrv}
%\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this 
% case
%% You must have a proper ".bib" file
%%  and remember to run:
%% latex bibtex latex latex
%% to resolve all references
%%
%% ACM needs 'a single self-contained file'!
%%
%%APPENDICES are optional
%%\balancecolumns
%\appendix
%%Appendix A
%\section{Headings in Appendices}
%The rules about hierarchical headings discussed above for
%the body of the article are different in the appendices.
%In the \textbf{appendix} environment, the command
%\textbf{section} is used to
%indicate the start of each Appendix, with alphabetic order
%designation (i.e. the first is A, the second B, etc.) and
%a title (if you include one).  So, if you need
%hierarchical structure
%\textit{within} an Appendix, start with \textbf{subsection} as the
%highest level. Here is an outline of the body of this
%document in Appendix-appropriate form:
%\subsection{Introduction}
%\subsection{The Body of the Paper}
%\subsubsection{Type Changes and  Special Characters}
%\subsubsection{Math Equations}
%\paragraph{Inline (In-text) Equations}
%\paragraph{Display Equations}
%\subsubsection{Citations}
%\subsubsection{Tables}
%\subsubsection{Figures}
%\subsubsection{Theorem-like Constructs}
%\subsubsection*{A Caveat for the \TeX\ Expert}
%\subsection{Conclusions}
%\subsection{Acknowledgments}
%\subsection{Additional Authors}
%This section is inserted by \LaTeX; you do not insert it.
%You just add the names and information in the
%\texttt{{\char'134}additionalauthors} command at the start
%of the document.
%\subsection{References}
%Generated by bibtex from your ~.bib file.  Run latex,
%then bibtex, then latex twice (to resolve references)
%to create the ~.bbl file.  Insert that ~.bbl file into
%the .tex source file and comment out
%the command \texttt{{\char'134}thebibliography}.
%% This next section command marks the start of
%% Appendix B, and does not continue the present hierarchy
%\section{More Help for the Hardy}
%The aamas2013 .cls file is based on the
%sig-alternate.cls file that is itself chock-full of succinct and
%helpful comments.  If you consider yourself a moderately experienced
%to expert user of \LaTeX, you may find reading it useful but please
%remember not to change it.
%%\balancecolumns % GM June 2007
%% That's all folks!
\end{document}
